Eclipse Che for Fair and Easy Education

### 2019-05-04 paper.tex
Transcribed sources

While this sounds harsh towards companies, I think unbiase education for students is not a nice thing to have, but a core concept of education in general. 

>>>>

While this sounds harsh towards companies, I think unbiased education for students is not a nice thing to have, but a core concept of education in general. 
